What to simulate? Inferring the right direction for mental rotation

### 2014-05-01 man/cogsci-2014/cogsci-2014.tex
Misc error fixes

In this paper, we explore these questions through rational analysis
\cite{Marr:1983to,anderson90,Shepard:1987tt} and compare four models
of mental rotation. We begin the paper by discussing the previous
literature on mental imagery. Next, we outline computational- and
algorithmic-level analyses of the problem of mental rotation.  We then
describe a behavioral experiment based on the classic mental rotation
studies \cite<e.g.,>{Cooper:1975wp}, and compare the results of our
experiment with each of the models. We conclude with a discussion of
the strengths and weaknesses of each model, and lay out directions for
future work.

@@

Active sampling is the idea people gather new information in a manner
that increases certainty about the problem space. An everyday example
of this can be observed in the game of ``20 questions'', in which one
person thinks of a concept, and another has to guess the concept in 20
questions or less. The first question is almost always ``person,
place, or thing?'', because the answer provides the most possible
information about the concept of interest. Active sampling has
gained support across several areas of cognitive science
\cite<e.g.,>{Gureckis:2012gu}, including other spatial domains
\cite{Juni:2011vo}. In the case of mental rotation, actively choosing
rotations may be the best way to gather evidence about the similarity
between the observed shapes when the angle of rotation is unknown.

@@

We recruited 247 participants on Amazon's Mechanical Turk using the
psiTurk experiment framework \cite{Mcdonnell12}. Each participant was
paid \$1.00 for 15 minutes of work, consisting of one block of 10
practice trials followed by two blocks of 100 randomly ordered
experiment trials.

>>>>

In this paper, we explore these questions through rational analysis
\cite{Marr:1983to,Anderson:1990,Shepard:1987tt} and compare four models
of mental rotation. We begin the paper by discussing the previous
literature on mental imagery. Next, we outline computational- and
algorithmic-level analyses of the problem of mental rotation.  We then
describe a behavioral experiment based on the classic mental rotation
studies \cite<e.g.,>{Cooper:1975wp}, and compare the results of our
experiment with each of the models. We conclude with a discussion of
the strengths and weaknesses of each model, and lay out directions for
future work.

@@

Active sampling is the idea that people gather new information in a
manner that increases certainty about the problem space. An everyday
example of this can be observed in the game of ``20 questions'', in
which one person thinks of a concept, and another has to guess the
concept in 20 questions or less. The first question is almost always
``person, place, or thing?'', because the answer provides the most
possible information about the concept of interest. Active sampling
has gained support across several areas of cognitive science
\cite<e.g.,>{Gureckis:2012gu}, including other spatial domains
\cite{Juni:2011vo}. In the case of mental rotation, actively choosing
rotations may be the best way to gather evidence about the similarity
between the observed shapes when the angle of rotation is unknown.

@@

We recruited 247 participants on Amazon's Mechanical Turk using the
psiTurk experiment framework \cite{McDonnell12}. Each participant was
paid \$1.00 for 15 minutes of work, consisting of one block of 10
practice trials followed by two blocks of 100 randomly ordered
experiment trials.
